---
title: "Lab 8"
author: "Claire Meuter"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, messsgae = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#attach packages 
library(tidyverse)
library(corrplot)
library(broom)
library(modelsummary)
library(here)
library(stargazer) #won't download?
```
## Read in data 
```{r}
homes <- read.csv(here("slo_homes.csv"))

```

make subset called homes_sub that only contains observations (rows) where the city is: 
- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt


```{r}
homes_sub <- homes %>%
  filter(City %in% c ("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```


## Do a little exploration of the data 


Summarry statistics (home price, based on city and sale status)
- Find and return in a nice sumary table the mean and standard deviation of home price, grouped by city and sale status

```{r, include=FALSE, eval = FALSE} 
# If i don't want to include this code I can do include = FAlSE 
summary_table <-  homes_sub %>%
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE), 
            sd_price = sd(Price, na.rm = TRUE))
view(summary_table)

#If I want to store but not run chunky code I can use eval = FALSE
```

Data visualization 
Home prices by city
```{r}
ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +  # work within aes is when it refers to an aesthic, if it's referring to a constant, ilke the alpha, it would go outside aes. Alpha refers to transparency of fill 
  scale_x_continuous(limits = c(0, 3e6)) #generic function to change conditions about x-axis IF it's continous 



```
# This plot is just exploratory- but we notice that it is similar to our data table. Ex- there is a higher densisty of lower priced homes in Santa Maria- so we might suggest it's cheaper to buy home in Santa Maria. When we visualize our data different ways, do we see the same things coming up?

# Another Task: Explore the relationship (visual data exploration) Between square footage and home price. Change the point color by city and the point shape by sale status

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) + geom_point(aes(color = City, shape = Status)) + geom_smooth(method = lm)
```

## Model the relationship with home prive as DV

Saturated model 
```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)
# looking at this data set- PricePerSquareFt is going to be redundant of price and SqFt. Other examples might be if there's going to be an obvious correlation between bathrooms and bedrooms

# Make a subset that only contains the quantative valiables 

homes_quant <- homes_sub %>%
  select(Price: PricePerSqFt)
homes_cor <- cor(homes_quant)
homes_cor
## If i want to make a corrlation plot I can do:
corrplot(homes_cor)


homes_lm1
```

# The way we interpret values in homes_lm1- if everything else is the same, I would expect a home in Atascadero to cost $9,068 less than a house in Arroyo Grande 
# How would I explore the diagnositic plots? 
```{r}
plot(homes_lm1)
```

# Lets try another model 

Try another model where we simplfy this a bit: 
Only include variables for 
- City
- SqFt
- Status 
```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)
homes_lm2 #call this to view 
plot(homes_lm2)
```
Let's talk about model fit- look at summary(homes_lm1)
we get 0.84 for R^2- this means that 84% of the variance in home price is explained by the variable predictors in this model 
That still means there's 16% of variables that explain variance that we don't have 
p-value: < 2.2e-16 

Let's look at our second model summary(homes_lm2)
This model only describes 52.68% of variance 
 
 Now we find the AIC value of each model 
```{r}
AIC(homes_lm1)
AIC(homes_lm2)

# A lower AIC values indicated a better balance between model fit and model complexity 
# Looking at our numbers- the first one is a better option, but we still have some read flags about using this one. So maybe we need to find an intermediate model that includes some different variables 
```
 
 ### so let's try another premuatation of this model that you think might make sense, check out and compare the model fit, outputs and AIC value 
```{r}
homes_lm3 <- lm(Price ~ City + Bedrooms + SqFt + Status, data = homes_sub)
plot(homes_lm3)
homes_lm3
summary(homes_lm3)
AIC(homes_lm3)
```
So this can help us think about how variables are related but none of them make a great model 

use `modelsummary` to show model outputs side-by-side: 
Heads up - if you use modelsummary to return outputs of multiple models, it wants you to feed it as a list 
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```
## Start making predictions with this model 

use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```
 
You can use the `preedict()` function to try out your model on new scenarios that you create 


How work in a branch and push changes: 
click on purple button in Git tab- make sure it says sync branch with remote- now you will see which branch you are working one 



